\section{Star Formation Rate}

On the study of far galaxies individual stellar spectrum is unresolved, is not 
possible to make a detailed census of the galaxy popullation. Only is possible 
to get information from the whole stellar population, an integrated spectrum.

Kennicutt pruposed a method in wich a linear relation between luminosity and 
SFR can be assumed. This model allows to estimate the young stars fraction and 
the mean SFR over periods of $10^8 - 10^9 \textrm{yr}$. The luminosity in the 
modfel, comes from the UV and the FIR broadband, also from speciffic 
recombination lines. 

In a typical galaxy spectrum the visible wavelengths are dominated by the main 
sequence stars (A to early F) and G-K giants. In few wavelength ranges we have 
a significative contribution from the young stars rather than the old stars. 
The infrared and far infrared wavelengths emission is dominated by dust, this 
dust is  heated by the whole stellar popullation, in particular by young, 
UV-bright stars \citep{law11}.The UV broadband emission is dominated by blue 
stars with temperature near to 40.000K. These hot and massive stars has a 
lifetime of $10^8\textrm{Gyr}$, they spend their nuclear fuel faster than smaller 
and cooler sunlike stars.

The relation between UV luminosity and Star Formation Rate \citep{kennicutt98} 
is given by:
  $ \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
\right)$
  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
  and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $

The UV dust absorption \citep{kennicutt09} is not taken account in this work.

%Synthesis Models:
%1) Study individual star spectra, star atmospheres. Creation of spectral 
%libraries.
%2) ``Individual stellar templates are summed together weigthed by an initial 
%mass function (IMF)... These isochrones can the be added in linear combination 
%to syntesize the spectrum or colors of a galaxy with any arbitrary star 
%formation history, usually parametrized as an expinential function of time.
%*** A single model contains at least 4 parameters (SF history, galaxy age, 
%metal abundance, and IMF). The colors of normal galaxies are well represented 
%by a one-parameter sequence with fixed age, composition and IMF, varying in the 
%time dependence of the SFR****





